---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---
This assignment makes use of data from a personal activity monitoring
device. This device collects data at 5 minute intervals through out the
day. The data consists of two months of data from an anonymous
individual collected during the months of October and November, 2012
and include the number of steps taken in 5 minute intervals each day.

```{r}
library(plyr)
library(ggplot2)
```

## Loading and preprocessing the data
The data used for this analysis is included in the Git repository with this report. The original raw data is
available in the activity.zip file located in the root level of the repository. The original file is available on the course web site here: [Activity monitoring data](https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip).

```{r}
unzip("activity.zip")
data <- read.csv("activity.csv")
data$date <- as.Date(data$date)
```

## What is mean total number of steps taken per day?
Ignoring missing values, show the total number of steps taken per day  
```{r}
data_summary <- ddply(data, c("date"), summarize,
                      total = sum(steps,na.rm = TRUE),
                      mean = mean(steps, na.rm = TRUE),
                      median = median(steps, na.rm = TRUE))

ggplot(data=data_summary,aes(x=date,y=total)) + geom_bar(stat="identity")
```

Calculate the mean and median for each day
```{r}

```


## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
